UCD\\MSc Thesis Proposal:\\\emph{Real-time Framework For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing}

### 2014-06-16 paper/proposal.tex
fixed intendation
initial bibliography paragraph

Most of the work in Capacity Planning for Cloud field is conducted from IaaS provider perspective. This paper will focus on SaaS provider who is charged on VM uptime rather than cpu, memory, i/o utlization. Moreover, VM uptime price varies based on renting strategy. This specific problem seems to be somewhat unexplored in the research area.

@@

\bibliographystyle{plain}
\bibliography{preproposal}

>>>>

Most of the work in Capacity Planning in cloud field is conducted from IaaS provider perspective (\bibitem{bib:join_pricing}). This paper will focus on SaaS provider who is charged on VM uptime rather than cpu, memory, i/o utlization. Moreover, VM uptime price varies based on renting strategy. This specific problem seems to be somewhat unexplored in the research area.

@@

\bibliographystyle{plain}
\bibliography{preproposal}
  \bibitem{bib:join_pricing} Ling Tang Sch. of Comput. Sci. & Eng., Nanjing Univ. of Sci. & Technol., Nanjing, China Jinghui Qian ; Lei Xu ; Yu Yan. Joint pricing and capacity planning for IaaS cloud. ICOIN, pages 34 - 39, 2014
  \end{preproposal}
